Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/design.tex
typo

\item Using the grammar to define both the \emph{external format} and the \emph{internal
    representation}, allowing the same grammar to be re-used in multiple applications, avoiding
  vulnerabilities like the Android Master Key.

\item Both parsing inputs into internal representations, as well as
      generating outputs from internal representations, without
      requiring the programmer to write any semantic actions. This prevents
      vulnerabilities such as the XNU bug, where format recognition and data processing
      are mixed and interact in unexpected ways.

>>>>

\item Using the grammar to define both the \emph{external format} and the \emph{internal
    representation}, allowing the same grammar to be re-used in multiple programs, avoiding
  vulnerabilities like the Android Master Key.

\item Both parsing inputs into internal representations, as well as
      generating outputs from internal representations, without
      requiring the programmer to write any semantic actions. This prevents
      vulnerabilities such as the XNU bug, where format recognition and semantics
      are mixed and interact in unexpected ways.
